---
title: "Amazon Case Study"
author: "Pragyan"
output: word_document
editor_options: 
  chunk_output_type: console
---
---
#==========================================================
## SET UP R MARKDOWN
#==========================================================
```{r}
rm(list = ls())
setwd("C:/A Pragyan/Rprograms")

# Load libraries
library(stargazer)
library(gdata)
library(ggplot2)
library(psych) 
library(ggeffects)
library(QuantPsyc)
library(lmtest)
library(usdm)
library(multiwayvcov)
library(sandwich)
library(foreign)
library(AER)
library(aod)
library(Rcpp)
library(mfx)
library(nnet)
library(reshape2)
library(msm)

# turn off scientific notation except for big numbers. 
options(scipen = 9)
```

#==========================================================
## READ AND EXPLORE DATA
#==========================================================
```{r}
## Loading data
mydata = read.csv("Amazon.csv", header = TRUE)

## Summary statistics
stargazer(mydata, type="text", median=TRUE, iqr=TRUE,digits=1, title="Descriptive Statistics")  
 
#check normalization
ggplot(mydata, aes(x=purchase)) + geom_histogram(colour="green") + stat_bin(binwidth = 5)
qqline(mydata$purchase, col=2)

## generates boxplot 
df <- data.frame(purchase=mydata$purchase, facebookvisit=as.factor(mydata$facebookvisit))
ggplot(df, aes(x=facebookvisit, y=purchase, fill=facebookvisit)) + geom_boxplot() + 
  xlab(" Facebook Visit") + ylab("Purchase Quantity") 

#Check collinearity #no correlation value > 0.8 
df2=mydata[c("distance","income","gender","facebookvisit","cust_age")]
round(cor(df2),3) 
vifcor(df2)

df61=mydata[c("numoffriends","numofposts","PublicProfile","purchase")]
round(cor(df61),3) 
vifcor(df61)



df3=mydata[c("distance","purchase","income","gender","facebookvisit","cust_age")]
describeBy(df3, df3$facebookvisit)

#mydata$facebookvisit<-factor(mydata$facebookvisit)
#is.factor(mydata$facebookvisit)

## Negative Binomial 
negbin1 <- glm.nb(purchase ~ distance+ income + cust_age + facebookvisit + gender, data = mydata)
#negbinlog <- glm.nb(log(purchase) ~ distance+ income + cust_age + facebookvisit + gender, data = mydata)


stargazer(negbin1, 
          apply.coef = exp, t.auto=F, p.auto = F,
          title="Negetive Binomial Results", type="text", 
          column.labels=c("IRRs"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001))

stargazer(negbin1, negbinlog,  
          title="Poisson Results", type="text", 
          column.labels=c("negbin1", "negbinlog"),
          df=FALSE, digits=3, star.cutoffs = c(0.05,0.01,0.001)) 


negbinempty<- glm.nb(purchase ~ 1, data = mydata)
lrtest(negbinempty, negbin1)

# test for heteroskadasticity
gqtest(negbin1) # Significant Goldfeld-Quandt test does not indicate heteroscedasticity 
bptest(negbin1) # Significant Breusch-Pagan test  indicates heteroscedasticity

consstder <- sqrt(diag(vcovHC(negbin1, type="const"))) # produces normal standard errors
HWrobstder <- sqrt(diag(vcovHC(negbin1, type="HC1"))) # produces Huber-White robust standard errors 

stargazer(negbin1, negbin1,  
          apply.coef = exp, t.auto=F, p.auto = F,
          se=list(consstder, HWrobstder),
          title="Negative Binomial Results with normalized", type="text", 
          column.labels=c("Normal SE", "HW-Robust SE"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001)) 

stargazer(negbin1,
          apply.coef = exp, t.auto=F, p.auto = F,
          se=list(HWrobstder),
          title="Negative Binomial Results with HW Robust SE", type="text", 
          column.labels=c("Negetive Binomial Results"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001))


#marginal effects

meffects4 <- ggpredict(negbin1, terms=c("facebookvisit")) 

ggplot(meffects4,aes(x, predicted)) + geom_point(size=4, colour="orange") + geom_line() +
 xlab("with or without  FB") + ylab("Predicted purchase quantity") +
 scale_x_continuous(breaks=c(0,1), labels=c("without FB", "with FB")) 

newdata <- with(mydata, data.frame(facebookvisit = seq(0,1), cust_age=mean(mydata$cust_age), distance=mean(mydata$distance),gender = mean(mydata$gender),income=mean(mydata$income)))

newdata$predicted_purchase <- predict(negbin1, newdata, type="response")
newdata$predicted_purchase <- predict(negbin1, newdata, type="response")


####
gqtest(negbin1) # Goldfeld-Quandt test indicates heteroscedasticity
bptest(negbin1) # Breusch-Pagan test indicates heteroscedasticity


HWrobstder <- sqrt(diag(vcovHC(negbin1, type="HC1"))) # produces Huber-White robust standard errors 

stargazer(negbin1, negbin1,  
          se=list(NULL, HWrobstder),
          title="Regression Results", type="text", 
          column.labels=c("Normal SE", "HW-Robust SE"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001))  # 


lrtest(poisson1, negbin1) #negbin 1 is better. there is overdisperson in the data

negbin1 <- glm.nb(purchase ~ distance+ income + cust_age + facebookvisit + gender, data = mydata)


####### gender and fbvisit interaction (not significant) ###
negbinintecraction1 <- glm.nb(purchase~income+facebookvisit*gender+distance+cust_age, data=mydata)

stargazer(negbinintecraction1, 
          apply.coef = exp, t.auto=F, p.auto = F,
          title="Regression Results", type="text", 
          column.labels=c("IRRs"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001))

meffects6 <- ggpredict(negbinintecraction1, terms=c("gender", "facebookvisit"))
ggplot(meffects6,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("gender") + ylab("Purchase") +
    labs(colour="facebookvisit") + 
    scale_colour_discrete(labels=c("No", "Yes")) +
    scale_x_continuous(breaks=c(0,1), labels=c("Male", "Female")) +
    theme(axis.title.x=element_blank())

meffects7 <- ggpredict(negbinintecraction1, terms=c("facebookvisit","gender"))
ggplot(meffects7,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("facebookvisit") + ylab("Purchase") +
    labs(colour="gender") + 
    scale_colour_discrete(labels=c("Male", "Female")) +
    scale_x_continuous(breaks=c(0,1), labels=c("No", "Yes")) +
    theme(axis.title.x=element_blank())



##Possion ##
poisson1 <- glm(purchase ~ distance+ income + cust_age + facebookvisit + gender, family="poisson", data=mydata)
poisson2 <- glm(purchase ~ distance+ income + cust_age + facebookvisit + gender + numoffriends + numofposts + PublicProfile, family="poisson", data=mydata)
poissonempty <- glm(purchase ~ 1, family="poisson", data=mydata)

stargazer(poissonempty, poisson1,poisson2,  
          title="Poisson Results", type="text", 
          column.labels=c("poissonempty", "poisson1", "poisson2"),
          df=FALSE, digits=3, star.cutoffs = c(0.05,0.01,0.001)) 

lrtest(poisson1, poissonempty) # possion is not a good fit
lrtest(poisson2, poissonempty) # possion is not a good fit
lrtest(poisson1, poisson2)



###########        Linear Model 

#OLS model with all variables
model0 <- lm(log(purchase)~income+gender+facebookvisit+distance+cust_age+numoffriends+numofposts+PublicProfile, data=mydata)

stargazer(model0,
          title="Regression Results", type="text", 
          column.labels=c("Model-0"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001)) 

#OLS model with reasonable variables
model1 <- lm(log(purchase)~facebookvisit+distance+income+gender+cust_age, data=mydata)
stargazer(model1,  
          title="Regression Results", type="text", 
          column.labels=c("Model-1"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001)) 

mydata$pred_purchase<-predict(model1) # let's look at the predicted purchase quantity for each observation in the data 

ggplot(mydata, aes(pred_purchase, fill = facebookvisit)) +
  geom_histogram(binwidth=.1, position="dodge")

range(mydata$pred_purchase)


#plot log purchase to check normalization
ggplot(mydata, aes(x=log(mydata$purchase))) + geom_histogram(colour="green")
qqnorm(log(mydata$purchase))
qqline(log(mydata$purchase), col=2)


##Endogenity
modelEndo1<- ivreg(purchase~ facebookvisit + distance+income+cust_age+gender | numoffriends+numofposts+PublicProfile+distance+income+cust_age+gender, data=mydata)
modelEndo2<- ivreg(log(purchase)~ facebookvisit + distance+income+cust_age+gender | numoffriends+numofposts+PublicProfile +distance+income+cust_age+gender, data=mydata)

#modelEndo3<- ivreg(log(purchase)~ distance+income+cust_age*facebookvisit+gender | numoffriends+numofposts+PublicProfile +distance+income+ cust_age*facebookvisit+ gender, data=mydata)



stargazer(modelEndo1, 
          title="2SLS Results", type="text", 
          column.labels=c("modelEndo1"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001))

summary(modelEndo1) # Durbin-Wu-Hausman test result
summary(modelEndo1,diagnostics = TRUE) #Instruments test


stargazer(modelEndo2, 
          title="2SLS Results", type="text", 
          column.labels=c("modelEndo2"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001))

summary(modelEndo2) # Durbin-Wu-Hausman test result
summary(modelEndo2,diagnostics = TRUE) #Instruments test


stargazer(modelEndo3, 
          title="2SLS Results", type="text", 
          column.labels=c("modelEndo3"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001))

summary(modelEndo3) # Durbin-Wu-Hausman test result
summary(modelEndo3,diagnostics = TRUE) #Instruments test



#interactions

modelintecraction1 <- lm(log(purchase)~income+gender+distance+facebookvisit*cust_age, data=mydata)

stargazer(modelintecraction1,
          title="Interaction Results", type="text", 
          column.labels=c("Model Intecraction 1"),
          df=FALSE, digits=2, star.cutoffs = c(0.05,0.01,0.001)) 

meffects1 <- ggpredict(modelintecraction1, terms=c("facebookvisit", "cust_age [29,34,39]"))

ggplot(meffects1,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("FBvisit") + ylab("Purchase") +
    labs(colour="cust age") + 
    scale_colour_discrete(labels=c("29", "34","39"))

modelintecraction2 <- lm(log(purchase)~income+facebookvisit*gender+distance+cust_age, data=mydata)
meffects2 <- ggpredict(modelintecraction2, terms=c("facebookvisit", "gender"))
ggplot(meffects2,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("facebookvisit") + ylab("Purchase") +
    labs(colour="gender") + 
    scale_colour_discrete(labels=c("Male", "Female")) +
    scale_x_continuous(breaks=c(0,1), labels=c("FB visit - No", "FB Visit- Yes")) +
    theme(axis.title.x=element_blank())

modelintecraction3 <- lm(log(purchase)~income+facebookvisit*gender+distance+cust_age, data=mydata)
meffects3 <- ggpredict(modelintecraction3, terms=c("gender", "facebookvisit"))
ggplot(meffects3,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("gender") + ylab("Purchase") +
    labs(colour="facebookvisit") + 
    scale_colour_discrete(labels=c("No", "Yes")) +
    scale_x_continuous(breaks=c(0,1), labels=c("Male", "Female")) +
    theme(axis.title.x=element_blank())


meffects2 <- ggpredict(modelintecraction2, terms=c("cust_age", "facebookvisit"))
ggplot(meffects1,aes(x, predicted, colour=group)) + geom_line(size=1.3) + 
    xlab("cust_age") + ylab("Purchase") +
    labs(colour="FBvisit") + 
    scale_colour_discrete(labels=c("No", "Yes"))


modelinteraction2 <- ivreg(log(purchase)~ distance+income+ cust_age*facebookvisit+gender | numoffriends+numofposts+PublicProfile +distance+income+ cust_age*facebookvisit+ gender, data=mydata)

meffects1 <- ggpredict(modelintecraction1, terms=c("cust_age", "facebookvisit")) # generates a tidy data frame  

## Model and tests with removed outliers
mydata2 = read.csv("Amazon2.csv", header = TRUE)
stargazer(mydata2, type="text", median=TRUE, iqr=TRUE,digits=1, title="Descriptive Statistics")
ggplot(mydata2, aes(x=purchase)) + geom_histogram(colour="green") + stat_bin(binwidth = 5)
describeBy(mydata2, mydata2$facebookvisit)

mydata2$facebookvisit<-factor(mydata$facebookvisit)
is.factor(mydata2$facebookvisit)

df3 <- data.frame(purchase=mydata2$purchase, facebookvisit=as.factor(mydata2$facebookvisit))
ggplot(df2, aes(x=facebookvisit, y=purchase, fill=facebookvisit)) + geom_boxplot() + 
  xlab(" Purchase through Facebook Visit") + ylab("Purchase Quantity") # generates boxplot

df3=mydata2[c("distance","income","gender","facebookvisit","cust_age","numoffriends" ,"numofposts" ,"PublicProfile")]
round(cor(df3),3) 
vifcor(df3) 

negbin100 <- glm.nb(purchase ~ distance+ income + cust_age + facebookvisit + gender, data = mydata2)


stargazer(negbin100, 
          apply.coef = exp, t.auto=F, p.auto = F,
          title="Negetive Binomial Results", type="text", 
          column.labels=c("IRRs"),
          df=FALSE, digits=4, star.cutoffs = c(0.05,0.01,0.001))